Sailing the High Seas: A Christian Exploration of Piracy

### 2024-04-28 paper.tex
Add metadata for generated pdf.
Use citeauthor

\makeatletter
\title{Sailing the High Seas: A Christian Exploration of Piracy}
\author{Pedro Avalos Jim\'enez}
\author{Niklas Anderson}
\affil{Wheaton College}
\date{\today}
\makeatother

@@

Take the restricted access to academic journal articles, for instance. Many academic
journals require all readers to pay not an insignificant sum to access research articles
that could contain insight that is valuable to the human race as a whole. Because of the
high cost of entry, certain groups are automatically excluded from reading and building
upon the research that has already been done. John Barlow puts the situation eloquently in
\citetitle{barlow:wine} when he says, \textcquote{barlow:wine}[.]{%
  I am not comfortable with a model which will restrict inquiry to the wealthy%
}
In the case of academic journal articles, why shouldn't anyone be able to better
themselves by consuming quality research articles? All humans should be allowed
to continue to learn more about God's creation without being bound by their
financial status. Just as how someone can go to the library and checkout any
book that tickles their fancy, they should be freely able to learn from the
ongoing research of our world. Of course one should recognize that not all
information is safe or helpful to be freely available on the internet, but that
is a topic for a later section.

A more concrete instance of where paywalls can be directly harmful to the human race is
with regards to medical research. Till et al. stresses how important access to medical
research is in their article \citetitle{till:medical-literature}.
\blockcquote{till:medical-literature}[.]{%
  Access to the medical literature is essential for both the practice of
  evidence-based medicine and meaningful contribution to medical sciences.
  Nonetheless, only 12\% of newly published papers are freely accessible online,
  and, as of 2014, only 3 million of the 26.3 million articles indexed on PubMed
  were available on the site's repository of free materials, PubMed Central.
  Access to paywall-protected literature remains primarily through institutional
  subscriptions. Such subscriptions are costly and many struggle to afford
  access. The result is a disparity in access to the medical literature,
  particularly for those in low-income and middle-income countries (LMICs)%
}
According to Till et al. the high subscription cost to access medical journal articles
means that those in less advantaged countries cannot afford access to the material, which
is detrimental to the furthering of medical sciences. In light of this, it should come as
no surprise that \textcquote{till:medical-literature}[.]{
  Nearly 1 million articles published by medical journals are downloaded on
  Sci-Hub each month%
} Piracy enables the less fortunate countries to access valuable medical data that is
essential to furthering medical research for the human race. In such a specific case as
this, it should not be controversial to conclude that piracy is a good thing.

@@

Regarding piracy and intellectual property laws, it is clear that the two are at odds with
one another. That being said, it is worth examining whether IP laws accomplish what they
seek to do: encourage innovation. Mark Lemley presents an argument against IP laws when he
writes, \blockcquote[1339]{lemley:faith-based}[.]{%
  \textins{IP} intervenes in the market to interfere with the freedom of others
  to do what they want in hopes of achieving the end of encouraging creativity.
  If we take that purpose out of the equation, we are left with a belief system
  that says the government should restrict your speech and freedom of action in
  favor of mine, not because doing so will improve the world, but simply because
  I spoke first%
}
To put it differently, intellectual property laws are based on the assumption that in
restricting who is allowed to have certain information, they are encouraging creativity
when, in reality, creativity does not always come first. IP laws are supposed to make
people want to work hard to get a good idea that they can have exclusive ownership of, but
having exclusive rights to an idea stifles further innovation. Under this system, only the
owner has the right to make changes. In fact, it seems that there would be more creativity
without IP laws. If everything was open to scrutiny and replication, there is bound to be
some improvement eventually because of all the people that could have a hand in making it
better. If a big streaming platform were to forfeit one of their IPs to the public, there
is no telling what kind of content could be created. In this way, piracy could allow for
the incremental improvement and scrutiny of conceptions, thus making them better.

@@

\subsubsection{Malware}
The intersection of trust and computing is not a new topic. Ken Thompson, the
creator of the Unix operating system, made this the topic of his Turing Award
lecture. In his lecture, he poses the question,
\textcquote[761]{thompson:trust}[.]{%
  to what extent should one trust a statement that
  a program is free of Trojan Horses? Perhaps it is more important to trust the
  people who wrote the software%
} With piracy, however, we add an additional actor in this chain of trust.
Thompson's lecture focuses solely on the developer-to-user relationship of
trust, with the assumption of an open-source project. Thompson, thus, comments
on how \textcquote[763]{thompson:trust}{%
  \textins{s}uch blatant code would not go undetected for long. Even the most
  casual perusal of the source of the C compiler would raise suspicions%
} When piracy is the method of distribution, however, the assumption of
equality between the source code and the delivered software does not hold. The
pirated software may have been tampered with, and the user has no simple way to
detect changes in the file(s) without doing some (often) complicated forensic
work. Although anti-malware tools may mitigate these issues, the problem of
trust still holds, and the anti-malware tools are not perfect. The character of
the seeder must be questioned, and it already stands on shaky ground if the
legality of their actions speaks for their moral compass and trustworthiness.

Piracy may openly distribute dangerous illegal content, but arguably the
larger threat is the dangerous content that remains undisclosed.
The relationship between piracy and malware distribution is not just a
theoretical argument against the use of piracy. Although research has remained
rather theoretical in this area, some researchers have performed empirical
studies to find a stronger link between more prevalent use of piracy and
malware presence. The study by Mezzour et al. reveals that piracy is not equal
around the globe, and it poses serious problems especially for people in
poor countries where piracy is widespread. Although they hypothesized, like
other researchers, that \enquote{cyber criminals would target rich countries}
because of monetary incentives, they found that, cyber criminals targeted
\textcquote{mezzour:empirical-study}[.]{%
  poor countries in Sub-Saharan Africa because of the low cost of attacking
  computers in this region%
} Mezzour et al. conclude that, due to the high correlation between piracy
and malware, one of the policy implications is that Sub-Saharan Africa requires
reducing piracy to combat the spread of malware.
In more recent news, Antivirus provider Kaspersky recently uncovered an example
of malware spreading through pirated software.~\cite{pcmag:malware}

\subsubsection{Response}
An argument based on malware distribution presents a strong case against piracy.
Moreover, we have to acknowledge that the problem targets those with less
resources (whether that be information, financial resources, or technical
resources) to protect themselves from the threats that malware poses. Piracy
circumvents mainline distribution channels that may incorporate secure policies
of data integrity, authenticity, and privacy. However, there are piracy tools
and sites that provide some ways to vet the authenticity of a user based on the
user's previous history and relationship with the piracy community. For example,
ThePirateBay, one of the most popular pirating sites, displays the status or
class of their users and holds these users to higher standards in order to
retain trust with the site's end users.~\cite{suprbay:status}

@@

The issue of trust is one that should not be unfamiliar to Christians. As
Christians, we have a Lord that we can trust in with all our hearts (Prov. 3:5).
As the Psalmist writes, \enquote{It is better to take refuge in the Lord than
to trust in man} (Ps. 118:8). Christians should be slow to put their entire
trust in metrics like those provided by ThePirateBay; while they provide some
founts of trust, they should not immediately encourage Christians to trust
piracy.

@@

There are few (if any) types of illegal content that are as immoral as that of
child pornography. It is a very sad reality, but this type of content is
distributed widely through the use of the Internet. Why and how this happens is
perhaps out of scope for this paper, but part of may be due to a sense of
privacy and anonymity that is fostered to an extreme in certain subcultures of
the Internet.~\cite[588]{prichard:subcultures} Research reveals that piracy and
piracy-adjacent tools provide the means to distribute this disgusting content
to unimaginable scales. Prichard et al explored this area of research, with
the following conclusions:
\blockcquote[593]{prichard:subcultures}{%
  Based on longitudinal data collected between August and November 2010, this
  study screened for the search terms that still appeared in the isoHunt Top
  300 list in November after being observed during August. In summary, the
  study found that 158/162 search terms related to infringing content, while
  3/162 search terms related to child pornography and 1/162 to bestiality%
}
These numbers may seem small to many. To properly interpret the above numbers,
consider that: 1) they do not represent the quantity of files that are shared
and 2) the researchers focused on isoHunt (which operated on the surface web)
and did not explore other means to find torrent files (i.e., means that utilize
the anonymity of the dark web). The numbers, rather, represent the consistent
interest within certain online subcultures in the immoral content. This
consistency presents a really compelling argument for Christians to question
piracy and the online culture that promotes and uses these methods.

\subsubsection{Response}
As mentioned above, Christians should not quickly dismiss this argument against
piracy. The reality of the matter is that we are sinful creatures full of
evil thoughts (Matt. 15:9); we are in dire need of a savior to redeem us, not
by any good works because even our best works are like filthy rags (Isa. 64:6).
This argument is compelling because of its severity. A naive response would
argue that harmful content is distributed via the surface web and without
piracy anyways. The argument, however, holds in that piracy enables the
widespread nature of this content, so what is a proper response to this
argument? There may be ways to engage with piracy communities to self-regulate
or to build better communities, as is suggested by Prichard et
al.~\cite[595--596]{prichard:subcultures}

>>>>

\makeatletter
\title{Sailing the High Seas: A Christian Exploration of Piracy}
\author{Pedro Avalos Jim\'enez}
\author{Niklas Anderson}
\affil{Wheaton College}
\date{\today}

\hypersetup{
  pdftitle={\@title},
  pdfauthor={Pedro Avalos Jim\'enez and Niklas Anderson},
  pdfsubject={piracy},
  pdfkeywords={%
    Christian, piracy, benefits, drawbacks, exploration, nuance, governance,
    privacy, malware, equal access, criminality, illegal content, economy%
  },
}
\makeatother

@@

Take the restricted access to academic journal articles, for instance. Many academic
journals require all readers to pay not an insignificant sum to access research articles
that could contain insight that is valuable to the human race as a whole. Because of the
high cost of entry, certain groups are automatically excluded from reading and building
upon the research that has already been done. \citeauthor{barlow:wine} puts the situation
eloquently in \citetitle{barlow:wine} when he says, \textcquote{barlow:wine}[.]{%
  I am not comfortable with a model which will restrict inquiry to the wealthy%
}
In the case of academic journal articles, why shouldn't anyone be able to better
themselves by consuming quality research articles? All humans should be allowed
to continue to learn more about God's creation without being bound by their
financial status. Just as how someone can go to the library and checkout any
book that tickles their fancy, they should be freely able to learn from the
ongoing research of our world. Of course one should recognize that not all
information is safe or helpful to be freely available on the internet, but that
is a topic for a later section.

A more concrete instance of where paywalls can be directly harmful to the human race is
with regards to medical research. \citeauthor{till:medical-literature} stresses how important
access to medical research is in their article \citetitle{till:medical-literature}.
\blockcquote{till:medical-literature}[.]{%
  Access to the medical literature is essential for both the practice of
  evidence-based medicine and meaningful contribution to medical sciences.
  Nonetheless, only 12\% of newly published papers are freely accessible online,
  and, as of 2014, only 3 million of the 26.3 million articles indexed on PubMed
  were available on the site's repository of free materials, PubMed Central.
  Access to paywall-protected literature remains primarily through institutional
  subscriptions. Such subscriptions are costly and many struggle to afford
  access. The result is a disparity in access to the medical literature,
  particularly for those in low-income and middle-income countries (LMICs)%
}
According to \citeauthor{till:medical-literature} the high subscription cost to access medical
journal articles means that those in less advantaged countries cannot afford access to the
material, which is detrimental to the furthering of medical sciences. In light of this, it
should come as no surprise that \textcquote{till:medical-literature}[.]{
  Nearly 1 million articles published by medical journals are downloaded on
  Sci-Hub each month%
} Piracy enables the less fortunate countries to access valuable medical data that is
essential to furthering medical research for the human race. In such a specific case as
this, it should not be controversial to conclude that piracy is a good thing.

@@

Regarding piracy and intellectual property laws, it is clear that the two are at odds with
one another. That being said, it is worth examining whether IP laws accomplish what they
seek to do: encourage innovation. \citeauthor{lemley:faith-based} presents an argument
against IP laws when he writes, \blockcquote[1339]{lemley:faith-based}[.]{%
  \textins{IP} intervenes in the market to interfere with the freedom of others
  to do what they want in hopes of achieving the end of encouraging creativity.
  If we take that purpose out of the equation, we are left with a belief system
  that says the government should restrict your speech and freedom of action in
  favor of mine, not because doing so will improve the world, but simply because
  I spoke first%
}
To put it differently, intellectual property laws are based on the assumption that in
restricting who is allowed to have certain information, they are encouraging creativity
when, in reality, creativity does not always come first. IP laws are supposed to make
people want to work hard to get a good idea that they can have exclusive ownership of, but
having exclusive rights to an idea stifles further innovation. Under this system, only the
owner has the right to make changes. In fact, it seems that there would be more creativity
without IP laws. If everything was open to scrutiny and replication, there is bound to be
some improvement eventually because of all the people that could have a hand in making it
better. If a big streaming platform were to forfeit one of their IPs to the public, there
is no telling what kind of content could be created. In this way, piracy could allow for
the incremental improvement and scrutiny of conceptions, thus making them better.

@@

\subsubsection{Malware}
The intersection of trust and computing is not a new topic.
\citeauthor{thompson:trust}, the creator of the Unix operating system, made this
the topic of his Turing Award lecture. In his lecture, he poses the question,
\textcquote[761]{thompson:trust}[.]{%
  to what extent should one trust a statement that
  a program is free of Trojan Horses? Perhaps it is more important to trust the
  people who wrote the software%
} With piracy, however, we add an additional actor in this chain of trust.
\citeauthor{thompson:trust} focuses solely on the developer-to-user relationship
of trust, with the assumption of an open-source project.
\citeauthor{thompson:trust}, thus, comments on how
\textcquote[763]{thompson:trust}{%
  \textins{s}uch blatant code would not go undetected for long. Even the most
  casual perusal of the source of the C compiler would raise suspicions%
} When piracy is the method of distribution, however, the assumption of
equality between the source code and the delivered software does not hold. The
pirated software may have been tampered with, and the user has no simple way to
detect changes in the file(s) without doing some (often) complicated forensic
work. Although anti-malware tools may mitigate these issues, the problem of
trust still holds, and the anti-malware tools are not perfect. The character of
the seeder must be questioned, and it already stands on shaky ground if the
legality of their actions speaks for their moral compass and trustworthiness.

Piracy may openly distribute dangerous illegal content, but arguably the
larger threat is the dangerous content that remains undisclosed.
The relationship between piracy and malware distribution is not just a
theoretical argument against the use of piracy. Although research has remained
rather theoretical in this area, some researchers have performed empirical
studies to find a stronger link between more prevalent use of piracy and
malware presence. The study by \citeauthor{mezzour:empirical-study} reveals that
piracy is not equal around the globe, and it poses serious problems especially
for people in poor countries where piracy is widespread. Although they
hypothesized, like other researchers, that \enquote{cyber criminals would target
rich countries} because of monetary incentives, they found that, cyber criminals
targeted \textcquote{mezzour:empirical-study}[.]{%
  poor countries in Sub-Saharan Africa because of the low cost of attacking
  computers in this region%
} \citeauthor{mezzour:empirical-study} concludes that, due to the high
correlation between piracy and malware, one of the policy implications is that
Sub-Saharan Africa requires reducing piracy to combat the spread of malware.
In more recent news, Antivirus provider Kaspersky recently uncovered an example
of malware spreading through pirated software.~\cite{pcmag:malware}

\subsubsection{Response}
An argument based on malware distribution presents a strong case against piracy.
Moreover, we have to acknowledge that the problem targets those with less
resources (whether that be information, financial resources, or technical
resources) to protect themselves from the threats that malware poses. Piracy
circumvents mainline distribution channels that may incorporate secure policies
of data integrity, authenticity, and privacy. However, there are piracy tools
and sites that provide some ways to vet the authenticity of a user based on the
user's previous history and relationship with the piracy community. For example,
\emph{ThePirateBay}, one of the most popular pirating sites, displays the status
or class of their users and holds these users to higher standards in order to
retain trust with the site's end users.~\cite{suprbay:status}

@@

The issue of trust is one that should not be unfamiliar to Christians. As
Christians, we have a Lord that we can trust in with all our hearts (Prov. 3:5).
As the Psalmist writes, \enquote{It is better to take refuge in the Lord than
to trust in man} (Ps. 118:8). Christians should be slow to put their entire
trust in metrics like those provided by \emph{ThePirateBay}; while they provide
some founts of trust, they should not immediately encourage Christians to trust
piracy.

@@

There are few (if any) types of illegal content that are as immoral as that of
child pornography. It is a very sad reality, but this type of content is
distributed widely through the use of the Internet. Why and how this happens is
perhaps out of scope for this paper, but part of may be due to a sense of
privacy and anonymity that is fostered to an extreme in certain subcultures of
the Internet.~\cite[588]{prichard:subcultures} Research reveals that piracy and
piracy-adjacent tools provide the means to distribute this disgusting content
to unimaginable scales. \citeauthor{prichard:subcultures} explored this area of
research, with the following conclusions:
\blockcquote[593]{prichard:subcultures}{%
  Based on longitudinal data collected between August and November 2010, this
  study screened for the search terms that still appeared in the isoHunt Top
  300 list in November after being observed during August. In summary, the
  study found that 158/162 search terms related to infringing content, while
  3/162 search terms related to child pornography and 1/162 to bestiality%
}
These numbers may seem small to many. To properly interpret the above numbers,
consider that: 1) they do not represent the quantity of files that are shared
and 2) the researchers focused on isoHunt (which operated on the surface web)
and did not explore other means to find torrent files (i.e., means that utilize
the anonymity of the dark web). The numbers, rather, represent the consistent
interest within certain online subcultures in the immoral content. This
consistency presents a really compelling argument for Christians to question
piracy and the online culture that promotes and uses these methods.

\subsubsection{Response}
As mentioned above, Christians should not quickly dismiss this argument against
piracy. The reality of the matter is that we are sinful creatures full of
evil thoughts (Matt. 15:9); we are in dire need of a savior to redeem us, not
by any good works because even our best works are like filthy rags (Isa. 64:6).
This argument is compelling because of its severity. A naive response would
argue that harmful content is distributed via the surface web and without
piracy anyways. The argument, however, holds in that piracy enables the
widespread nature of this content, so what is a proper response to this
argument? There may be ways to engage with piracy communities to self-regulate
or to build better communities, as is suggested by
\citeauthor{prichard:subcultures}.~\cite[595--596]{prichard:subcultures}
